---
title: "Best Coding Practices"
output: html_notebook
editor_options: 
  markdown: 
    wrap: 72
---

*held at the Faculty of Economics of the Masaryk University on 19.03.2023*

Please be informed I didn't solve some issues regarding the running of bash
scripts in this R Notebook. To complete the first set of tasks, please run the 
Colab notebook [here](https://github.com/VondracekS/ESF_Workshop_BestCodingPractices).


# R Coding part

In this part, you'll get an opportunity to try some of the concepts we've covered during presentation.

```{r}
getwd()
```
In this section, you will perform the following tasks:  

- iteratively search through a directory and subsequently load the data
- test of the loaded data
- using a modular design, you will separate functionalities into operation-specific functions



```{r}
# TODO: Create a function that:
# - loads all the .csv files from the directory 
# - stores them in a dictionary;
# - add some explanatory docstring
#
# hints: os.listdir, string.split, make sure you read only csv files, 
# btw: is the function name the best possible one? change this eventually

read_csv <- function(path){
  csv_list = list()
  return(NULL)
}

```

Please feel free to test your function:

```{r}
test_read_csv <- function(path) {
  # Test for the read.csv method
  dict_full <- read_csv(path)
  assertthat::assert_that(length(dict_full) == length(list.files(path, pattern = ".csv")))
  cat(sprintf("Tests passed for the test_read_csv(%s)\n", path))
}
```



OK, now you have the function. However, some improvements are still possible.
PLease finish the following tasks:  

- adjust the fuction to ignore the "0" padding for all numbers smaller than 100 
(e.g. "050" will be replaced by "50" and so on) -> read_csv_v2()
- separate the padding removal to another function -> remove_padding()
- write a test for the padding removal
- use the remove_padding() function within the read_csv_v3
- extend the function to be able to specify only particular .csv files to be read (and if not specified, just load all) -> read_csv_v4()

Again, please find more suitable names for all the variables


```{r}
# TODO: ignore the padding within the function
# hint: did you know that "011" integer will be read as "11"?

read_csv_v2 <- function(path){
  csv_list = list()
  return(NULL)
}
```


```{r}
# TODO: separating the padding removal function

remove_padding <- function(tgt_str){
  return(NULL)
}
```

```{r}
test_remove_padding <- function(test_cases=c('0125', '1250')) {
  assertthat::assert_that(remove_padding(test_cases[1]) == '125')
  cat(sprintf("remove_padding(%s) -> %s Test OK\n", test_cases[1], remove_padding(test_cases[1])))
  assertthat::assert_that(remove_padding(test_cases[2]) == '1250')
  cat(sprintf("remove_padding(%s) -> %s Test OK\n", test_cases[2], remove_padding(test_cases[2])))
}
```



```{r}
# TODO: adjust the former function so that you use the padding removal
read_csv_v3 <- function(path){
  csv_list = list()
  return(NULL)
}
```


```{r}

read_csv_v4 <- function(path){
  csv_list = list()
  return(NULL)
}

```

In the last part, create a new function, called get_monitor()
This function will do the following:  

- load the specific monitoring stations
- concatenate all data frames from the dictionary
- if dropna, the function will drop all na values for all loaded tables
- if print_stats, the function will print descriptive stats for all the data frames
- if plot, the function will plot all variables in a single plot (
  i.e. Date will be on the x axis, concentration on the y axis, ID will be in the plot title


```{r}
# TODO: get_monitor function
# Hints: 
# -separate functionalities (loading the data and plotting the data)
# -use already defined function that loads the csv data

get_monitor <- function(station_ids, dropna=TRUE, plot=TRUE) {
  stations_data <- NULL
  if (dropna) {return(NULL)}
  if (plot) {return(NULL)}
  return(stations_data)
}
```



